The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-05 paper.tex
Reworked the end of the intro and the begining of section 2

@@

Existing benchmarks (robocup at home) have issues -- the next challenge for HRI
is to tackle complex, unpredictable situations -> free play

This task is based on free child-robot interactions (free play) in a
\emph{sandboxed} environment: while the interaction is free (children do not
have a particular task to perform, except to play), the activity is scaffolded
by a specific apparatus (a large touchscreen) where the interaction take place.
Capturing the entirety of the interaction is consequently possible and
practical. We present in the remaining of the paper the methodology and
experimental procedure associated to the free-play task, as well as the main
analyses that can be conducted on the collected data (including a new annotation
scheme for social interaction).

children can engage in open-ended and
non-directive play situations, yet sufficiently
defined to be reproducible;

\subsection{Background on social play}

The choice of a playful interaction is supported by the wealth of social
situations and social behaviours that \emph{play} elicits. Most of the research
in that field builds on the precursory work of Parten who established five
\emph{stages of play}~\cite{parten1932social}:

\begin{enumerate}
    \item {\bf Solitary (independent) play}: Playing separately from
        others, with no reference to what others are doing.
    \item {\bf Onlooker play}: Watching others play. May engage in
        conversation but not engaged in doing. True focus on the children at
        play.
    \item {\bf Parallel play} (adjacent play, social co-action): Playing
        with similar objects, clearly beside others but not with them (near
        but not with others.)
    \item {\bf Associative play}:  Playing with others without
        organization of play activity. Initiating or responding to
        interaction with peers. 
    \item {\bf Cooperative play}: Coordinating one's behavior with that
        of a peer. Everyone has a role, with the emergence of a sense of
        belonging to a group. Beginning of "team work."
\end{enumerate}

\todo{Should the age be added?}

These five stages of play have been extensively discussed and refined over the
last century, yet remain remarkably widely accepted as such, and to the ears of
researchers in social robotics, they may resonate as an implicit roadmap.

\subsection{Framing: face-to-face dyadic and sandboxed child-robot interactions}

To mitigate the technical challenges presented by free play interactions in
their most unconstrained version (like high dimensionality and uncertainties),
we have developed a \emph{free play sandbox}, Figure~\ref{fig|freeplay}: a large
touchscreen (60cm $\times$ 33cm) is used as an interactive surface
(\emph{sandtray} paradigm~\cite{baxter2012touchscreen}). Two agents (either a
pair of children or one child and one robot) play together by freely moving on a
2D plane items (characters and blocks, see Figure~\ref{fig|sandbox}). A
background image depicts a generic empty environment, with different symbolic
zones (water, grass, path, bushes...). Additionally, the children can draw on
the background using a tool applying a color on their touches. The players do
not have any particular task to complete, they are simply invited to freely
play.

@@

\subsection{Task}
description of the task and why it fills a gap in the literature/tools used so
far (provide clearer,  and interesting setup, \emph{easy} to reuse)

@@

>>>>

We introduce in this paper such a task, designed to elicit rich, complex, varied
social interactions while being well suited for interactions with robots and
supporting rigorous scientific methodologies.

@@

Our interaction paradigm is based on free and playful interactions (free play)
in a \emph{sandboxed} environment: while the interaction is free (participants
are not directed to perform any particular task beyond playing), the activity is
both \emph{scaffolded} and \emph{constrained} by the setup mediating the
interaction (essentially, a large table-top touchscreen).
Participant engage in open-ended and non-directive play situations, yet sufficiently
well defined to be reproducible and practical to record and analyse.

This initial description frames the socio-cognitive interactions that might be
observed and studied: playful, dyadic, face-to-face interactions. While gestures
and manipulations (including joint manipulations) play an important role in this
paradigm, the participants do not typically move much during the interaction.
Because it builds on play, this paradigm is also naturally suited to the study
of child-child and child-robot interactions.

The choice of a playful interaction is supported by the wealth of social
situations and social behaviours that \emph{play} elicits. Most of the research
in that field builds on the precursory work of Parten who established five
\emph{stages of play}~\cite{parten1932social}, corresponding to different stages
of development, and accordingly associated to typical age ranges:

\begin{enumerate}
    \item {\bf Solitary (independent) play}, age 2-3: Playing separately from
        others, with no reference to what others are doing.
    \item {\bf Onlooker play}, age 2.5-3.5: Watching others play. May engage in
        conversation but not engaged in doing. True focus on the children at
        play.
    \item {\bf Parallel play} (adjacent play, social co-action), age 2.5-3.5: Playing
        with similar objects, clearly beside others but not with them (near
        but not with others.)
    \item {\bf Associative play}, age 3-4:  Playing with others without
        organization of play activity. Initiating or responding to
        interaction with peers. 
    \item {\bf Cooperative play}, age 4+: Coordinating one's behavior with that
        of a peer. Everyone has a role, with the emergence of a sense of
        belonging to a group. Beginning of "team work."
\end{enumerate}

These five stages of play have been extensively discussed and refined over the
last century, yet remain remarkably widely accepted as such. It must be noted
that the age ranges are only indicative. In particular, most of the early
behaviours still occur at times by older children.

Interestingly, these five stages can been looked at from the perspective of HRI
as well. They certainly evoke a roadmap for the development of human-robot
social interactions.

@@

\subsection{Task}

To mitigate the technical challenges presented by free play interactions in
their most unconstrained version (like high dimensionality and uncertainties),
we have developed a \emph{free-play sandbox}, Figure~\ref{fig|freeplay}: a large
touchscreen (60cm $\times$ 33cm) is used as an interactive surface
(\emph{sandtray} paradigm~\cite{baxter2012touchscreen}). Two participants (either a
pair of children or one child and one robot) play together by freely moving on a
2D plane items (characters and blocks, see Figure~\ref{fig|sandbox}). A
background image depicts a generic empty environment, with different symbolic
zones (water, grass, path, bushes...). Additionally, the children can draw on
the background using a tool applying a color on their touches. The players do
not have any particular task to complete, they are simply invited to freely
play. Importantly, they can play for as long as they wish (for
practical reasons, we have limited the sessions to a maximum of 40 minutes in
our own experiments, see Section~\ref{sec:dataset}).

Capturing all the interactions taking place during the play sessions is possible
and practical with this setup. Even though the children will typically move a
little, the task is fundamentally a face-to-face, spatially delimited,
interaction, and as such simplifies the data collection. For instance, during
our dataset acquisition campaign (120 children, more than 45h of footage), the
children's faces were automatically detected in 97\% [TODO: check that!] of the
recorded frames.

@@

TODO: percentage faces seen?
